On the presentation of orthogonal groups over polynomial rings

### 2019-04-30 dl-paper.tex
Minor fix

Throughout this section $\Phi$ is a simply-laced irreducible root system and $A$ is a local ring with maximal ideal $M$.
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by
 $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.

@@

\subsection{The proof of the injectivity theorem}

 \begin{comment}
\begin{lemma} if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$. \end{lemma}
\begin{proof}
 Lol
\end{proof}
\end{comment}

@@

\begin{comment}
($\alpha = 21$, $\beta = 1r$, $\alpha + \beta = 2r$)
($\alpha = 21$, $\beta = 13$, $\alpha + \beta = 23$)
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & -bX^{-1} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
\left(\begin{array}{ccc} 
 1 & 0 & * \\
 0 & 1 & * \\
 mX & m'X & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & \frac{bX^{-1}}{1 - bm} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & -bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - mb)^{-1} 
 \end{array}\right) = S_\beta(-b, g^+).
\end{multline}
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 -a & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = x_\alpha(-a) \cdot S_\beta(-b, g^+)
\end{multline}
\begin{multline}
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 (1  - bm)^{-1} & 0 & 0 \\
 0 & 1 & 0 \\
 0 & 0 & 1 - bm 
 \end{array}\right)
\left(\begin{array}{ccc} 
 1 + abm' & 0 & 0 \\
 0 & (1 + abm')^{-1} & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 a(1 + abm') & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = \\
 = 
 \left(\begin{array}{ccc} 
 1 & - \frac{bm'}{1 + abm'} & * \\
 0 & 1 & * \\
 \frac{(m + m'a)X}{1 - bm} & \frac{m'X}{1 + abm'} & 1 
 \end{array}\right)
\end{multline}

There is still a mistake in the last implication :(
\end{comment}
Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.
\begin{multline}
[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
 T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\frac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
 \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
 = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
 \begin{multline} h' = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\
 \sim  h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
 = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\frac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
 h\cdot x_{\alpha + \beta}\left(\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
\end{multline}

>>>>

Throughout this section $\Phi$ is a simply-laced irreducible root system and $A$ is a local ring with maximal ideal $M$.

@@

\subsection{The proof of the injectivity theorem}
We denote by $B$ the ring $M[X] + A[X^{-1}]$ considered as a graded subring of $A[X, X^{-1}]$.
Denote by $\overline{G}^{\geq 0}_M$ the image of the map $\St(\Phi, R[X], M[X]) \to \St(\Phi, A[X, X^{-1}])$ and by
 $G^{\leq 0}$ the group $\St(\Phi, A[X^{-1}])$.

\begin{lemma} if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$. \end{lemma}
\begin{proof}
 Lol
\end{proof}

@@

\begin{comment}
($\alpha = 21$, $\beta = 1r$, $\alpha + \beta = 2r$)
($\alpha = 21$, $\beta = 13$, $\alpha + \beta = 23$)
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & -bX^{-1} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
\left(\begin{array}{ccc} 
 1 & 0 & * \\
 0 & 1 & * \\
 mX & m'X & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & \frac{bX^{-1}}{1 - bm} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & -bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - mb)^{-1} 
 \end{array}\right) = S_\beta(-b, g^+).
\end{multline}
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 -a & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = x_\alpha(-a) \cdot S_\beta(-b, g^+)
\end{multline}
\begin{multline}
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 (1  - bm)^{-1} & 0 & 0 \\
 0 & 1 & 0 \\
 0 & 0 & 1 - bm 
 \end{array}\right)
\left(\begin{array}{ccc} 
 1 + abm' & 0 & 0 \\
 0 & (1 + abm')^{-1} & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 a(1 + abm') & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = \\
 = 
 \left(\begin{array}{ccc} 
 1 & - \frac{bm'}{1 + abm'} & * \\
 0 & 1 & * \\
 \frac{(m + m'a)X}{1 - bm} & \frac{m'X}{1 + abm'} & 1 
 \end{array}\right)
\end{multline}
\end{comment}

There is still a mistake in the last implication :(
Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.
\begin{multline}
[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
 T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\frac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
 \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
 = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
 \begin{multline} h' = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\
 \sim  h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
 = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\frac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
 h\cdot x_{\alpha + \beta}\left(\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
\end{multline}
